Influences of GDP in the U.S

### 2022-11-14 Manuscript/manuscript.tex
commit

\section*{Discussion}

- violate homoscedacty assumption

>>>>

\section*{Discussion}
In practice, there are many economic indicators that impact GDP. 
There is no unique set of factors discovered yet that predict GDP. 
This paper showed that TCMR, DPI, UNRATE, and BSPL have a significant relationship with GDP.
These variables were selected with subjectivity, and this is important to take into consideration. 
This paper did not show any significant relationship between Total Primary Energy Consumption and GDP in the United States. 
It is also important to consider that the homoscedacy assumption of OLS Regression is questionable in this paper. 
For future studies, to limit this violation the data could be transformed.
This research is a introductory study into the relationship between energy consumption and economic growth. 
This could be a useful start point for economic developers to identify signals of crucial moments to allow policy makers to make more informed decisions.
